---
output:
  reprex::reprex_document:
    venue: "gh"
    advertise: FALSE
    session_info: TRUE
    style: TRUE
    comment: "#;-)"
    tidyverse_quiet: TRUE
    std_out_err: TRUE
knit: reprex::reprex_render
---

# emmeans cant evaluate averaging object

<!-- badges: start -->
<!-- badges: end -->

The problem is that emmeans gives an error when evaluating an averaging object form the MuMIn package, even when it says it should in this [link](https://cran.r-project.org/web/packages/emmeans/vignettes/models.html) I have been trying to debug this for a couple of days with no luck. All data and code is in [this repo](https://github.com/derek-corcoran-barrios/emmeansProblem)

first we load the needed r packages and the dataset

```{r}
library(emmeans)
library(lme4)
library(MuMIn)
library(doParallel)

Data <- readRDS("Data.rds")
```

Now we fit a general model:

```{r}
Model <- glmer(richness ~ aspect + elevation + 
                     initial_habitat  +
                       I(abs(year - 1)) +
                       I((year-1)^2) +
                     slope +
                     treatment:initial_habitat +
                     year:initial_habitat +
                     year:treatment + 
                     year:treatment:initial_habitat + 
                     (1 | block_no), family = poisson, data = Data, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
```


And we make a model selection (skip this step since it takes a while, the "SelectRichness.rds" file is in [this](https://github.com/derek-corcoran-barrios/emmeansProblem) github)

```{r, cache = T, message=F, error=F}
options(na.action = "na.fail")

library(doParallel)
cl <- makeCluster(4) 
registerDoParallel(cl)

clusterEvalQ(cl, library(lme4))
clusterExport(cl, "Data")

Select <- MuMIn::pdredge(Model, extra = list(R2m = function(x) r.squaredGLMM(x)[1, 1], R2c = function(x) r.squaredGLMM(x)[1, 2]),fixed = ~YEAR:Treatment, cluster = cl)

stopCluster(cl)

saveRDS(Select, "SelectRichness.rds")
```

And now we Select the best models, I will do this twice, since the outcome of the `subset` function will be used to show how the best model does not have issues and the averaged model from `get.models` which is the result I need is not working  

```{r, cache = T}
Select <- readRDS("SelectRichness.rds")
Selected <- subset(Select, delta < 2)
SelectedList <- get.models(Select, delta < 2)
```

## Working with the best model works

As specified above the goal is to find if the treatments do yieald differences by year 4, based on the model. So first we will show this with the best model

```{r}
BestModel <- get.models(Selected, 1)[[1]]

noise.emm <- emmeans(BestModel, pairwise ~ year  + initial_habitat +  initial_habitat:year + year:treatment, at = list(year = 4), data = Data)

pairs(noise.emm, simple = "treatment") |> 
  as.data.frame() |>  dplyr::filter(p.value < 0.05) |> 
  dplyr::arrange(initial_habitat, estimate) |> 
  dplyr::select(-SE, -df, -z.ratio) |> 
  knitr::kable()
```

## Working with the average model does not works

This does not work 

```{r}
AV <- model.avg(SelectedList, fit = TRUE)

noise.emm_av <- emmeans(AV, pairwise ~ year  + initial_habitat +  initial_habitat:year + year:treatment, at = list(year = 4), data = Data)

pairs(noise.emm_av, simple = "treatment") |> 
  as.data.frame() |>  dplyr::filter(p.value < 0.05) |> 
  dplyr::arrange(initial_habitat, estimate) |> 
  dplyr::select(-SE, -df, -z.ratio) |> 
  knitr::kable()
```
